### 2017-02-27 intro.tex
Add .gitignore and macro \cpnote{...}.

By shifting $H_1,H_2,\ldots,H_k$ from $\pubaux$ to $\privaux$, we do
not change the functionality, but we may very well change the
security profile of the resulting Bloom-filter variant.  Indeed,
this is the case.  When $H_1,H_2,\ldots,H_K$ are assumed to be
pseudorandom functions, we can prove that this variant achieves a
sort of ``semantic security'' privacy guarantee: the bit array~$M$
leaks a good approximation of~$|S|$, but nothing more.  (Such a
result is not possible for the standard Bloom filter, or any other
data structure with empty~$\privaux$.)

@@

\ignore{We provide various security notions for these primitives...
FP with private, public representation coins; set privacy with
private, public representation coins; FP/set privacy in the
multi-representation setting (outsider attack, think CDNs); FP/set
privacy in the multi-representation setting with corruptions
(insider attack, think P2P networks) \tsnote{Those are just the ones
that come to mind now.  Could also consider authenticity of
representations, think CDN or P2P settings.}}

>>>>

By shifting $H_1,H_2,\ldots,H_k$ from $\pubaux$ to $\privaux$, we do
not change the functionality, but we may very well change the
security profile of the resulting Bloom-filter variant.  Indeed,
this is the case.  When $H_1,H_2,\ldots,H_K$
%
\cpnote{Is $K$ supposed to be $k$?}
%
are assumed to be pseudorandom functions, we can prove that this variant
achieves a sort of ``semantic security'' privacy guarantee: the bit array~$M$
leaks a good approximation of~$|S|$, but nothing more.  (Such a result is not
possible for the standard Bloom filter, or any other data structure with
empty~$\privaux$.)

@@

 ignore{We provide various security notions for these primitives...
FP with private, public representation coins; set privacy with
private, public representation coins; FP/set privacy in the
multi-representation setting (outsider attack, think CDNs); FP/set
privacy in the multi-representation setting with corruptions
(insider attack, think P2P networks) \tsnote{Those are just the ones
that come to mind now.  Could also consider authenticity of
representations, think CDN or P2P settings.}}
